Assertion Contracts

### 2022-02-17 papers/assertion-contract/paper.tex
update 4.2

The Converter generate a on/off-chain assertion program in Solidity as the follows.

@@

For sorted array

@@

For a heap

@@

Coprimes number

>>>>

\subsubsection{Examples.} The Converter generate a on/off-chain assertion program in Solidity as the follows.

\paragraph{Prime numbers.}{ on/off-chain assertion program for primes numbers}

@@

\paragraph{Sorted arrays.}{ on/off-chain assertion program for sorted arrays}

@@

\paragraph{Heaps.}{ on/off-chain assertion program for heap arrays}

@@

\paragraph{Coprime numbers.}{ on/off-chain assertion program for coprime numbers}
